The Galactic Midplane is Not a Plane: Implications for {\em Gaia}

### 2019-04-16 paper/ms.tex
Add schmactions many orbit plot to paper, and update caption

\begin{figure*}
\plotone{fig/schmactions_many_orbits.pdf}
\caption{We report one half the 95\uth{} minus 5\uth{} percentile of the error in the
measured action ($\Delta J_i$) from coordinate system errors for the thin,
thick, and halo orbits (Table~\ref{tab:orbits}). See discussion in the text for the justification in using this to measure the magnitude of the induced error. The {\em left}, {\em center},
and {\em right} panels show the result for $J_r$, $L_z$, and $J_z$,
respectively. The {\em upper} panels consider an offset in $z$ and the {\em
lower} panels consider an offset in $x$ (equivalently, an offset in the Solar
radius).}
\label{fig:many_orbit_wrong_ref}
\end{figure*}

>>>>

\begin{figure*}
\plotone{fig/schmactions_many_orbits.pdf}
\caption{We report one half the 95\uth{} minus 5\uth{} percentile of the error in the
measured action ($\Delta J_i$) from coordinate system errors for the thin,
thick, and halo orbits (Table~\ref{tab:orbits}). See discussion in the text for the justification in using this to measure the magnitude of the induced error. The {\em left}, {\em center},
and {\em right} panels show the result for $J_r$, $L_z$, and $J_z$,
respectively. The {\em upper} panels consider an offset in $z$ and the {\em
lower} panels consider an offset in $x$ (equivalently, an offset in the Solar
radius). In some panels we also plot as dashed lines the epicyclic prediction of the induced action error (Equations~\ref{eq:actions_epi_error}~and~\ref{eq:Jr_epi_dx}). In the epicyclic approximation, a $z$ offset only induces an error in $J_z$ --- for all three orbits the epicyclic approximation is a good description of the $J_z$ error. An $x$ offset induces an error in $J_r$ and $L_z$. The error in $J_r$ is somewhat well-described for the thin-disk and thick-disk orbits, and a poor description for the halo orbit. For $L_z$, the epicyclic approximation is not a good description for any orbit.}
\label{fig:many_orbit_wrong_ref}
\end{figure*}
